\documentclass[]{weekly-report}
\usepackage{hyperref}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% BEGINNING %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%
%%% Input your name, student number, 
%%% project and report details

\def\studentname{Philip Corr}
\def\projecttitle{ConvNets for iOS Gesture Recognition Applications}
\def\ucdstudentnumber{12318581}
\def\weeklyreportnumber{5}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%ss
%%% First Section  

\section{Update}

\begin{itemize}

\item Got an Iphone 6. Doesn't have force touch as that is only on 6s and above. Will have to work with what I have for now anyway.

\item Currently working on sequence to sequence RNN to see if I can detect numbers with multiple digits. This is mainly to facilitate learning more about tensorflow. It may proove to be some nice extra functionality in my project though.

\item Added unicode flags to iOS app. Trying to make the user interface more appealing and user friendly. 

\item Looking more into tensorboard also. Seems like it will be an indispensible tool to have in terms of getting a deeper understanding of the NN's I create.  
	
\end{itemize}

\section{Items for discussion}

\begin{itemize}

\item Best way to show the unicode flags?

\item Talk through mnist with summmaries code and how it links to tensorboard.

\item data persistance in iOS?

\end{itemize}

\section{Plan for Next Week}
In order of priority from top to bottom

\begin{itemize}
\item Make a timetable for the year, more detailed one until christmas?

\item Get permission to record data

\item Sequence to sequence neural network running

\item Start into further deep learning resources e.g.~\cite{Ng-Coursera-2016, VincentVanhoucke-Udacity-2016, Nvidia-DL-Course-2016}. Tensorflow also.

\item Investigate paramaterisation of bitmaps.

\end{itemize}

\section{Meeting Notes}


hoffe transform - ellipse

Youtube videos on ios recognition

keep on top of lit review

Need to get on top of NN's and tensorboard for presentation

sequence to sequence

600

ios versions

Use Siri to speak numbers

%%%%%%%%%%%%%%%%%%%%%%
%%% Bibliography

\bibliography{report-biblio}{}
\bibliographystyle{IEEEtran}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{last_page}

 \end{document} 