\documentclass[]{weekly-report}
\usepackage{hyperref}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% BEGINNING %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%
%%% Input your name, student number, 
%%% project and report details

\def\studentname{Philip Corr}
\def\projecttitle{ConvNets for iOS Gesture Recognition Applications}
\def\ucdstudentnumber{12318581}
\def\weeklyreportnumber{6}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%ss
%%% First Section  

\section{Update}

\begin{itemize}

\item Set up Xcode and built happiness app from stanford module~\cite{PaulHegarty2016}. App went through how to set up gestures and auto-layout.

\item Went through convolutional.py from the tensorflow website in more detail. 
	
\end{itemize}

\section{Items for discussion}

\begin{itemize}

\item Have everything I need to make the app now

\item Is it ok to record meetings electronically in Latex and provide it as supplement to my lab book? What is log-book folder/documentation folder for? Doesn't it have to be hard copy?

\item Need to get an Iphone. Is it 4 or above? Ipad type? Ipod touch?

\end{itemize}

\section{Plan for Next Week}
In order of priority from top to bottom

\begin{itemize}
\item Get permission to record data

\item Get app up and running.

\item Make a timetable for the year, more detailed one until christmas?

\item Start into further deep learning resources e.g.~\cite{Ng-Coursera-2016, VincentVanhoucke-Udacity-2016, Nvidia-DL-Course-2016}. Tensorflow also.

\item Investigate paramaterisation of bitmaps.

\end{itemize}

\section{Meeting Notes}

Paul:
ffmpeg - scale down images

hoffe transform - ellipse

Youtube videos on ios recognition

keep on top of lit review

Need to get on top of NN's and tensorboard for presentation

sequence to sequence

600

ios versions
get an iphone device...


%%%%%%%%%%%%%%%%%%%%%%
%%% Bibliography

\bibliography{report-biblio}{}
\bibliographystyle{IEEEtran}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{last_page}

 \end{document} 